Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2015-07-15 tmm.tex
modify authors information

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (e-mail: shengbin@pku.edu.cn; sunjun@pku.edu.cn; duanyizhou@pku.edu.cn; guozongming@pku.edu.cn).}}

>>>>

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (Email: shengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn; Phone: +86 1082529615; Fax: +86 1082529207).}}
